%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Talks}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cvtalkseries
    {Designing tools for 3D content authoring based on 3D sketching}
    {\begin{cvtalks}
        \item {\cvtalk
            {University of California Santa Barbara -- \textit{hosted by Jennifer Jacobs and Tobias Höllerer}}
            {Santa Barbara (USA)} % Place
            {Aug. 2023} % Date
            }
        \item {\cvtalk
            {University of British Columbia -- \textit{hosted by Alla Sheffer}}
            {Vancouver (Canada)} % Place
            {Jul. 2023} % Date
            }
    \end{cvtalks}}

%---------------------------------------------------------

\cvtalkseries
    {VideoDoodles: Hand-Drawn Animations on Videos with Scene-Aware Canvases}
    {\begin{cvtalks}
        \item {\cvtalk
            {SIGGRAPH 2023 -- \textit{Technical Paper presentation}}
            {Los Angeles (USA)} % Place
            {Aug. 2023} % Date
            }
        \item {\cvtalk
            {Inria ex)situ lab -- \textit{hosted by Theophanis Tsandilas and Wendy Mackay}}
            {Palaiseau (France)} % Place
            {May 2023} % Date
            }
        \item {\cvtalk
            {Inria MFX lab -- \textit{hosted by Sylvain Lefebvre}}
            {Nancy (France)} % Place
            {May 2023} % Date
            }
        \item {\cvtalk
            {Technical University of Denmark Christmas Workshop 2022  -- \textit{hosted by J. Andreas Bærentzen}}
            {Lyngby (Denmark)} % Place
            {Dec 2022} % Date
            }
    \end{cvtalks}}

%---------------------------------------------------------

\cvtalkseries
    {VR Sketching for Surface Modeling}
    {\begin{cvtalks}
        \item {\cvtalk
            {University of Surrey SketchX virtual seminar -- \textit{hosted by Yulia Gryadistskaya}}
            {Virtual} % Place
            {Sep. 2022} % Date
            }
    \end{cvtalks}}
    
%---------------------------------------------------------
\cvtalkseries
    {Piecewise-Smooth Surface Fitting onto Unstructured 3D Sketches}
    {\begin{cvtalks}
        \item {\cvtalk
            {SIGGRAPH 2022 -- \textit{Technical Paper presentation}}
            {Vancouver (Canada)} % Place
            {Aug. 2022} % Date
            }
    \end{cvtalks}}

%---------------------------------------------------------
\cvtalkseries
    {CASSIE: Curve And Surface Sketching in Immersive Environments}
    {\begin{cvtalks}
        \item {\cvtalk
            {Toronto Geometry Colloquium -- \textit{opener talk}}
            {Virtual} % Place
            {Oct. 2021} % Date
            }
        \item {\cvtalk
            {CHI 2021 -- \textit{Technical Paper presentation}}
            {Virtual} % Place
            {May. 2021} % Date
            }
        \item {\cvtalk
            {JFIG (French computer graphics conference) 2020 -- \textit{Technical Paper presentation}}
            {Virtual} % Place
            {Nov. 2020} % Date
            }
    \end{cvtalks}}

%---------------------------------------------------------
\end{cventries}
